### 2017-02-22 MSSM/MSSM.tex
More editing

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\phi} = 160\,\GeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.png}}
\subfloat[$m_{\phi} = 2.9\,\TeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.png}}
%\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}
%\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
\end{center}
\caption[Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi$
production process with decay into $\Pgt\Pgt$ as a function of tau isolation 
working point and \mT~selection, for two mass points.]{Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi$ production process with decay into $\Pgt\Pgt$,
as a function of tau isolation working point (from very loose to very very tight) and
of \mT~selection from \mT~$<20\,\GeV$ to \mT~$<40\,\GeV$, normalised to the best limit in the plane, indicated by the asterisk. This is shown
for (a) $m_{\phi} = 160\,\GeV$ and (b) $m_{\phi} = 2.9\,\TeV$. The most optimal combination of \mT~selection and 
hadronic tau isolation working point varies, with looser selections preferred at higher mass.}
\label{fig:mssm_selection_mt_taumt}
\end{figure}
~
\begin{figure}[h!]
\begin{center}
\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_mt.pdf}}
\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_mt.pdf}}
\end{center}
\caption[Pre-fit expected limits on \xsbr for the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$
processes
in the
\mutau channel for an increasingly looser \mT~selection and tau isolation
working point.]{Pre-fit expected limits on \xsbr in the \mutau channel for (a) $\Pg\Pg\phi$ and
(b) $\Pbottom\Pbottom\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
at the tight working point and \mT~$<30\,\GeV$ in green, the medium working point and \mT~$<40\,\GeV$ in red,
the loose working point and \mT~$<50\,\GeV$ in blue and the very loose working point and \mT~$<60\,\GeV$ in black. Loosening
the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
degrades them at low mass.}
\label{fig:mssm_gradcuts_mt}
\end{figure}

These figures show that looser selections are preferred for higher masses. This behaviour can be
explained by considering the function of each of the selections. Tightening the hadronic
tau isolation working point reduces the selection of fake taus and increases the proportion
of backgrounds which contain real hadronic taus. The \mT~selection reduces
the \Wjets background. As the backgrounds are concentrated at the lower
end of the spectrum of mass-like discriminating variables, such tighter
selections are preferred where signal and backgrounds overlap. For higher masses the
backgrounds are lower in the region where the signal peaks,
and there is more benefit to loosening the selection
to increase the signal efficiency than to keep the tighter selection
to reduce an already low background.
The selection was optimised for masses around $800\,\GeV$--$1\,\TeV$, by
using the medium hadronic tau isolation working point and a selection on \mT~$<40\,\GeV$.

The choice of the hadronic tau \pT~selection is driven by the effect on the low mass region:
raising the \pT~selection by $10\,\GeV$ from the minimum of $20\,\GeV$ does not affect the sensivity
of the analysis for high mass points, while recovering some of the loss of loosening 
tau isolation working point and \mT~cut. The reason for this is that when using \pT~$>30\,\GeV$ 
fewer background events are selected. The effect of the increased hadronic tau \pT~selection on the 
upper limits for the $\Pg\Pg\phi$ production process is shown
in figure \ref{fig:mssm_tauptcut}a, and on the $\Pbottom\Pbottom\phi$ production process
in figure \ref{fig:mssm_tauptcut}b. At low mass the improvement in the $\Pg\Pg\phi$ limits
obtained by increasing the \pT~selection is sizeable, for $\Pbottom\Pbottom\phi$ events the effect is much
less pronounced.

\begin{figure}[h!]
\begin{center}
\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_ggH_remake.pdf}}
\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_bbH_remake.pdf}}
\end{center}
\caption[Pre-fit expected limits on \xsbr in the
\mutau channel for $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ production, comparing
different hadronic tau \pT~cuts.]{Pre-fit expected limits on \xsbr in the \mutau channel for (a) $\Pg\Pg\phi$ production and (b) $\Pbottom\Pbottom\phi$ production. The
limits when using the medium hadronic tau isolation working point and \mT~$<40\,\GeV$ selection using a minimum
hadronic tau \pT~selection of $20\,\GeV$ (red circles), $30\,\GeV$ (blue circles) and $40\,\GeV$ (black circles) are shown. The green
circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
the $\Pg\Pg\phi$ production process improve at low masses when increasing the minimum hadronic tau \pT~selection,
the effect on the $\Pbottom\Pbottom\phi$ production process is less pronounced.}
\label{fig:mssm_tauptcut}
\end{figure}

\subsection{\texorpdfstring{Event selection in the \etau channel}{Event selection in the e tau channel}}
\label{sec:mssm_eventsel_et}
For selection of events in the \etau channel, the first step is
a trigger that only requires an electron at \ac{L1}. Loose ID and isolation
criteria are made on the electron with the \ac{HLT}.

The offline event selection requires an oppositely charged
electron and hadronically decaying tau, which are well-separated ($\Delta R > 0.5$).
The minimum \pT~of the electron is required to be $26\,\GeV$, with $|\eta| < 2.1$. %due to trigger conditions
The impact parameters of the electron are required to satisfy
$d_{xy} < 0.045\,\cm$ and $d_{z} < 0.2\,\cm$, and the electron
must pass additional identification criteria. The working point of the
MVA identification discriminator that is used corresponds to a cut on the discriminator
which selects electrons from \Zee events with 80\% efficiency. In addition the
electron needs to be isolated, $I_{\text{rel}}^{\Pe} < 0.1$, with the relative isolation variable calculated with a cone size of 0.3.

The hadronic tau is required to have a \pT~greater than $30\,\GeV$, $|\eta|<2.3$,
and is required to be reconstructed by the HPS algorithm and to pass the medium
working point of the MVA isolation discriminator. The impact parameter $d_{z}$ of the
hadronic tau must be less than $0.2\,\cm$.
Finally, the hadronic tau must 
pass the tight working point of the anti-electron discriminator
and the loose working point of the anti-muon discriminator.

Analogously to the muons, it was found that the analysis is not highly sensitive
to the choice of electron isolation variable and cut value.
A topological selection on the \mT~variable is also made in this channel to reject \Wjets events. 
The value of \mT~$< 50\,\GeV$ that is used is obtained by performing a 2D optimisation where the \mT~selection
and hadronic tau isolation working point are varied at the same time. The same considerations as
for the \mutau channel apply, as illustrated in figure \ref{fig:mssm_gradcuts_et}.
The choice of the hadronic tau \pT~selection of $30\,\GeV$ is
made to recover some of the sensitivity lost at low mass by using looser \mT~and hadronic
tau isolation criteria. This is illustrated in figure \ref{fig:mssm_tauptcut_et}.

\begin{figure}[h!]
\begin{center}
\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_et.pdf}}
\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_et.pdf}}
\end{center}
\caption[Pre-fit expected limits on \xsbr in the \etau
channel for $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ production for an increasingly
looser \mT~selection and tau isolation working point.]{Pre-fit expected limits on \xsbr in the \etau channel for (a) $\Pg\Pg\phi$ and
(b) $\Pbottom\Pbottom\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
at the tight working point and \mT~$<40\,\GeV$ in green, the medium working point and \mT~$<50\,\GeV$ in red,
the loose working point and \mT~$<60\,\GeV$ in blue and the very loose working point and \mT~$<70\,\GeV$ in black. Loosening
the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
degrades them at low mass.}
\label{fig:mssm_gradcuts_et}
\end{figure}
\begin{figure}[h!]
\begin{center}
\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_ggH_remake.pdf}}
\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_bbH_remake.pdf}}
\end{center}
\caption[Pre-fit expected limits on \xsbr in the \etau
channel for $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ production comparing different
hadronic tau isolation cuts.]{Pre-fit expected limits on \xsbr in the \etau channel for (a) $\Pg\Pg\phi$ production and (b) $\Pbottom\Pbottom\phi$ production. The
limits using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
hadronic tau \pT~cut of $20\,\GeV$ (red circles), $30\,\GeV$ (blue circles) and $40\,\GeV$ (black circles) are shown. The green
circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
the $\Pg\Pg\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
the effect on the $\Pbottom\Pbottom\phi$ production process is less pronounced.}
\label{fig:mssm_tauptcut_et}
\end{figure}

\subsection{\texorpdfstring{Event selection in the \tautau channel}{Event selection in the tau tau channel}}
\label{sec:mssm_eventsel_tt}
The trigger in the \tautau channel requires two hadronic taus at \ac{L1} and the \ac{HLT}
applies loose identification and isolation criteria to these hadronic taus.

The offline event selection requires both hadronic taus to be oppositely charged, separated
by $\Delta R > 0.5$, have \pT~of at least $40\,\GeV$ and satisfy $|\eta|<2.1$. Both taus need
to be reconstructed by the HPS algorithm, and their impact parameter $d_{z}$ must be less than $0.2\,\cm$.
Both taus need to pass the tight working point of the isolation discriminator, the very loose 
working point of the anti-electron discriminator and the loose working point of the anti-muon discriminator. 
The tight working point of the isolation discriminator is chosen such that
the channel is near-optimal at high mass, while not losing too much sensitivity in the low--intermediate mass range.
This is illustrated in figure \ref{fig:mssm_tauid_tt} for the $\Pg\Pg\phi$ process.

\begin{figure}[h!]
\begin{center}
\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_thesis_ttopt_ggH.pdf}}
\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_thesis_ttopt_bbH.pdf}}
\end{center}
\caption[Expected upper limits for the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ process
in the \tautau channel, comparing different hadronic tau isolation working
points.]{Expected upper limits for (a) the $\Pg\Pg\phi$ process and (b) the $\Pbottom\Pbottom\phi$ process 
in the \tautau channel, using the 
medium (green), tight (red) and very tight working point of the tau isolation discriminator.
The pattern is roughly the same as in the \etau and \mutau channels, with looser selections preferred at high
mass.}
\label{fig:mssm_tauid_tt}
\end{figure}

\subsection{\texorpdfstring{Event selection in the \emu channel}{Event selection in the e mu channel}}
\label{sec:mssm_eventsel_em}
Events in the \emu channel are first selected by two triggers
that both require an electron and muon at \ac{L1} and apply loose ID and
isolation requirements to these objects at \ac{HLT}. The \pT~requirements on
the electron and muon are different in the two triggers, thus using the combination of the two
improves the signal efficiency.

Offline, the electron and muon are required to be oppositely charged
and separated by $\Delta R >0.3$.
The electron needs to have a minimum \pT~of $13\,\GeV$ and have $|\eta|< 2.5$. As
in the \etau channel the electron's impact parameters have to 
satisfy $d_{xy} < 0.045\,\cm$ and $d_{z}<0.2\,\cm$. The additional
identification requirement is identical to the criterium applied to electrons in the \etau channel.
The electron also needs to be isolated, $I_{\text{rel}}^{\Pe}<0.15$, where the relative isolation variable is calculated
with a cone size of 0.3.

The muon needs to have a \pT~of at least $10\,\GeV$, $|\eta|<2.4$ and 
its impact parameters need to be $d_{xy}<0.045\,\cm$ and $d_{z}<0.2\,\cm$.
In addition to the kinematic requirements the muon must
pass the medium identification criteria and be isolated with $I_{\text{rel}}^{\Pgm} < 0.2$,
where the relative isolation variable is calculated using a cone size of 0.4.

Because a combination of triggers is used, one with electron \pT~$> 23\,\GeV$ and muon \pT~$>8\,\GeV$ 
and one with muon \pT~$> 23\,\GeV$ and electron \pT~$> 13\,\GeV$, the object firing
the higher \pT~trigger leg needs to have a transverse momentum
of at least $24\,\GeV$ on top of the requirements already discussed. This avoids
events in the lower part of the trigger turn-on curve being selected.

In addition to the selection described so far,
 a topological selection is made on the $D_{\zeta}$ variable \cite{cdf-dzeta},
\begin{align}\label{eqn:mssm_em_dzeta}
D_{\zeta} = P_{\zeta} - 1.85 P_{\zeta}^{\text{vis}}, \notag \\
\text{where } P_{\zeta} = (\vec{p}_{\text{T},1}^{\text{  vis}} + \vec{p}_{\text{T},2}^{\text{  vis}} + E_{\text{T}}^{\text{miss}})\frac{\vec{\zeta}}{|\vec{\zeta}|}, \notag \\
\text{and } P_{\zeta}^{\text{vis}} = (\vec{p}_{\text{T},1}^{\text{  vis}}+\vec{p}_{\text{T},2}^{\text{  vis}})\frac{\vec{\zeta}}{|\vec{\zeta}|}.
\end{align}
This means $D_{\zeta}$ is defined as the projection of the transverse momenta of the visible tau decay products plus missing energy \pT+\MET~onto 
the axis $\vec{\zeta}$, minus the projection of only the transverse momenta of the visible tau decay products onto this axis.
The axis $\vec{\zeta}$ is the axis that bisects
the directions $\vec{p}_{\text{T,1}}^{\text{  vis}}$ and $\vec{p}_{\text{T,2}}^{\text{  vis}}$
of the visible decay products in the transverse plane. This definition is illustrated in figure
\ref{fig:mssm_dzeta}a, with figure \ref{fig:mssm_dzeta}b showing the $D_{\zeta}$ distribution
for \emu events. The selection used, $D_{\zeta} > -20\,\GeV$, rejects $\ttbar$, \Wjets and diboson
events. 
%The momentum of the neutrinos should not be in the opposite direction of the sum of the visible decay products
%as the neutrinos and visible tau decay products travel at small angles from the original tau.

\begin{figure}[h!]
\begin{center}
\subfloat[Reconstruction of $D_{\zeta}$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/PZeta.pdf}}
\subfloat[$D_{\zeta}$ distribution in \emu channel]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/pzeta_inclusive_em_2016.pdf}}
\end{center}
\caption[Reconstruction of the $D_{\zeta}$ variable and the $D_{\zeta}$ distribution
in the \emu channel.]{(a) reconstruction of $D_{\zeta}$ \cite{cdf-dzeta} and (b) $D_{\zeta}$ distribution in the 
\emu channel\cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_dzeta}
\end{figure}
~\clearpage
\subsection{Categorisation}
\label{sec:mssm_eventsel_categories}
As the analysis targets both the gluon fusion
and the b-associated production modes, 
the sensitivity to the signal can be increased by categorising
based on the number of b-tagged jets in the event.

>>>>

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\phi} = 160\,\GeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.png}}
\subfloat[$m_{\phi} = 2.9\,\TeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.png}}
%\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}
%\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
\end{center}
\caption[Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi$
production process with decay into $\Pgt\Pgt$ as a function of tau isolation 
working point and \mT~selection, for two mass points.]{Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi\rightarrow\Pgt\Pgt$ process,
as a function of the tau isolation working point (from very loose to very very tight) and
of the \mT~selection from $\mTm<20\,\GeV$ to $\mTm<40\,\GeV$, normalised to the best limit in the plane, indicated by the asterisk. This is shown
for (a) $m_{\phi} = 160\,\GeV$ and (b) $m_{\phi} = 2.9\,\TeV$. The most optimal combination of \mT~selection and 
hadronic tau isolation working point varies, with looser selections preferred at higher mass.}
\label{fig:mssm_selection_mt_taumt}
\end{figure}
~
\begin{figure}[h!]
\begin{center}
\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_mt.pdf}}
\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_mt.pdf}}
\end{center}
\caption[Pre-fit expected limits on \xsbr for the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$
processes
in the
\mutau channel for an increasingly looser \mT~selection and tau isolation
working point.]{Pre-fit expected limits on \xsbr in the \mutau channel for (a) $\Pg\Pg\phi$ and
(b) $\Pbottom\Pbottom\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
at the tight working point and $\mTm<30\,\GeV$ in green, the medium working point and $\mTm<40\,\GeV$ in red,
the loose working point and $\mTm<50\,\GeV$ in blue and the very loose working point and $\mTm<60\,\GeV$ in black. Loosening
the tau isolation working point and \mT~selection improves the limits at higher mass and
degrades them at low mass.}
\label{fig:mssm_gradcuts_mt}
\end{figure}

These figures show that looser selections are preferred for higher masses. This behaviour can be
explained by considering the function of each of the selections. Tightening the hadronic
tau isolation working point reduces the selection of fake taus and increases the proportion
of backgrounds which contain real hadronic taus. The \mT~selection reduces
the \Wjets background. As the backgrounds are concentrated at the lower
end of the spectrum of mass-like discriminating variables, such tighter
selections are preferred where signal and backgrounds overlap. For higher masses the
backgrounds are lower in the region where the signal peaks,
and there is more benefit to loosening the selection
to increase the signal efficiency than to keep the tighter selection
to reduce an already low background.
The selection was optimised for masses around $800\,\GeV$--$1\,\TeV$, by
using the medium hadronic tau isolation working point and a selection on $\mTm<40\,\GeV$.

The choice of the hadronic tau \pT~selection is driven by the effect on the low mass region:
raising the \pT~selection by $10\,\GeV$ from the minimum of $20\,\GeV$ does not affect the sensivity
of the analysis for high mass points, while recovering some of the loss of loosening 
the tau isolation working point and \mT~cut. The reason for this is that when using $\pTm >30\,\GeV$ 
the loss of background events exceeds the loss of signal events. The effect of the increased hadronic tau \pT~selection on the 
upper limits for the $\Pg\Pg\phi$ production process is shown
in figure~\ref{fig:mssm_tauptcut}a, and on the $\Pbottom\Pbottom\phi$ production process
in figure~ \ref{fig:mssm_tauptcut}b. At low mass the improvement in the $\Pg\Pg\phi$ limits
obtained by increasing the \pT~selection is sizeable; for $\Pbottom\Pbottom\phi$ events the effect is much
less pronounced.

\begin{figure}[h!]
\begin{center}
\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_ggH_remake.pdf}}
\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_bbH_remake.pdf}}
\end{center}
\caption[Pre-fit expected limits on \xsbr in the
\mutau channel for $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ production, comparing
different hadronic tau \pT~cuts.]{Pre-fit expected limits on \xsbr in the \mutau channel for (a) $\Pg\Pg\phi$ production and (b) $\Pbottom\Pbottom\phi$ production. The
limits when using the medium hadronic tau isolation working point and $\mTm <40\,\GeV$ selection using a minimum
hadronic tau \pT~selection of $20\,\GeV$ (red circles), $30\,\GeV$ (blue circles) and $40\,\GeV$ (black circles) are shown. The green
circles show the limits using the tight tau isolation working point and $\mTm<30\,\GeV$. The limits on
the $\Pg\Pg\phi$ production process improve at low masses when increasing the minimum hadronic tau \pT~selection,
the effect on the $\Pbottom\Pbottom\phi$ production process is less pronounced.}
\label{fig:mssm_tauptcut}
\end{figure}

\subsection{\texorpdfstring{Event selection in the \etau channel}{Event selection in the e tau channel}}
\label{sec:mssm_eventsel_et}
For selection of events in the \etau channel, the first step is
a trigger that only requires an electron at \ac{L1}. Loose ID and isolation
criteria are applied to the electron with the \ac{HLT}.

The offline event selection requires an oppositely charged
electron and hadronically decaying tau, which are separated by $\Delta R > 0.5$.
The minimum electron is required to have $\pTm >26\,\GeV$ and $|\eta| < 2.1$. %due to trigger conditions
The impact parameters are required to satisfy
$d_{xy} < 0.045\,\cm$ and $d_{z} < 0.2\,\cm$, and the electron
must pass additional identification criteria. The chosen working point of the
MVA identification discriminator was designed
to select electrons from \Zee events with 80\% efficiency. In addition the
electron needs to be isolated, $I_{\text{rel}}^{\Pe} < 0.1$, with the relative isolation variable calculated with a cone size of 0.3.

The hadronic tau is required to have $\pTm > 30\,\GeV$, $|\eta|<2.3$,
to be reconstructed by the HPS algorithm and to pass the medium
working point of the MVA isolation discriminator. The impact parameter $d_{z}$ of the
hadronic tau must be less than $0.2\,\cm$.
Finally, the hadronic tau must 
pass the tight working point of the anti-electron discriminator
and the loose working point of the anti-muon discriminator.

Analogously to the muons, it was found that the analysis is not highly sensitive
to the choice of electron isolation variable and cut value.
A topological selection on the \mT~variable is also made in this channel to reject \Wjets events. 
The value of $\mTm< 50\,\GeV$ that is used is obtained by performing a simultaneous optimisation of the \mT~selection
and hadronic tau isolation working point. The same considerations as
for the \mutau channel apply, as illustrated in figure \ref{fig:mssm_gradcuts_et}.
The choice of the hadronic tau \pT~selection of $30\,\GeV$ is
made to recover some of the sensitivity lost at low mass by using looser \mT~and hadronic
tau isolation criteria. This is illustrated in figure \ref{fig:mssm_tauptcut_et}.

\begin{figure}[h!]
\begin{center}
\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_et.pdf}}
\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_et.pdf}}
\end{center}
\caption[Pre-fit expected limits on \xsbr in the \etau
channel for $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ production for an increasingly
looser \mT~selection and tau isolation working point.]{Pre-fit expected limits on \xsbr in the \etau channel for (a) $\Pg\Pg\phi$ and
(b) $\Pbottom\Pbottom\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
at the tight working point and $\mTm<40\,\GeV$ in green, the medium working point and $\mTm<50\,\GeV$ in red,
the loose working point and $\mTm<60\,\GeV$ in blue and the very loose working point and $\mTm <70\,\GeV$ in black. Loosening
the tau isolation working point and \mT~selection improves the limits at higher mass and
degrades them at low mass.}
\label{fig:mssm_gradcuts_et}
\end{figure}
\begin{figure}[h!]
\begin{center}
\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_ggH_remake.pdf}}
\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_bbH_remake.pdf}}
\end{center}
\caption[Pre-fit expected limits on \xsbr in the \etau
channel for $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ production comparing different
hadronic tau isolation cuts.]{Pre-fit expected limits on \xsbr in the \etau channel for (a) $\Pg\Pg\phi$ production and (b) $\Pbottom\Pbottom\phi$ production. The
limits using the medium hadronic tau isolation working point and $\mTm<40$ GeV selection using a minimum
hadronic tau \pT~cut of $20\,\GeV$ (red circles), $30\,\GeV$ (blue circles) and $40\,\GeV$ (black circles) are shown. The green
circles show the limits using the tight tau isolation working point and $\mTm<40\,\GeV$. The limits on
the $\Pg\Pg\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
the effect on the $\Pbottom\Pbottom\phi$ production process is less pronounced.}
\label{fig:mssm_tauptcut_et}
\end{figure}

\subsection{\texorpdfstring{Event selection in the \tautau channel}{Event selection in the tau tau channel}}
\label{sec:mssm_eventsel_tt}
The trigger in the \tautau channel requires two hadronic taus at \ac{L1} to which loose identification
and isolation criteria are applied in the \ac{HLT}

The offline event selection requires both hadronic taus to be oppositely charged, separated
by $\Delta R > 0.5$, to have $\pTm>40\,\GeV$ and to satisfy $|\eta|<2.1$. Both taus need
to be reconstructed by the HPS algorithm, and their impact parameter $d_{z}$ must be less than $0.2\,\cm$.
Both taus need to pass the tight working point of the isolation discriminator, the very loose 
working point of the anti-electron discriminator and the loose working point of the anti-muon discriminator. 
The tight working point of the isolation discriminator is chosen such that
the channel is near-optimal at high mass, while not losing too much sensitivity in the low to intermediate mass range.
This is illustrated in figure \ref{fig:mssm_tauid_tt}a for the $\Pg\Pg\phi$ process and in figure \ref{fig:mssm_tauid_tt}b for the $\Pbottom\Pbottom\phi$ process.

\begin{figure}[h!]
\begin{center}
\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_thesis_ttopt_ggH.pdf}}
\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_thesis_ttopt_bbH.pdf}}
\end{center}
\caption[Expected upper limits for the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ process
in the \tautau channel, comparing different hadronic tau isolation working
points.]{Expected upper limits for (a) the $\Pg\Pg\phi$ process and (b) the $\Pbottom\Pbottom\phi$ process 
in the \tautau channel, using the 
medium (green), tight (red) and very tight working point of the tau isolation discriminator.
The pattern is similar to that in the \etau and \mutau channels, with looser selections preferred at high
mass.}
\label{fig:mssm_tauid_tt}
\end{figure}

\subsection{\texorpdfstring{Event selection in the \emu channel}{Event selection in the e mu channel}}
\label{sec:mssm_eventsel_em}
Events in the \emu channel are first selected by two triggers
that both require an electron and muon at \ac{L1} and apply loose ID and
isolation requirements to these objects in the \ac{HLT}. The \pT~requirements on
the electron and muon are different in the two triggers, thus using the combination of the two
improves the signal efficiency.

Offline, the electron and muon are required to be oppositely charged
and separated by $\Delta R > 0.3$.
The electron needs to have $\pTm>13\,\GeV$ and $|\eta|< 2.5$. As
in the \etau channel the impact parameters have to 
satisfy $d_{xy} < 0.045\,\cm$ and $d_{z}<0.2\,\cm$. The same selection 
on the MVA identification discriminator as in the \etau channel is applied.
The electron also needs to be isolated, $I_{\text{rel}}^{\Pe}<0.15$, where the relative isolation variable is calculated
with a cone size of 0.3.

The muon needs to have $\pTm>10\,\GeV$, $|\eta|<2.4$ and 
its impact parameters need to be $d_{xy}<0.045\,\cm$ and $d_{z}<0.2\,\cm$.
In addition to these requirements the muon must
pass the ``medium'' identification criteria and be isolated with $I_{\text{rel}}^{\Pgm} < 0.2$,
where the relative isolation variable is calculated using a cone size of 0.4.

Because a combination of triggers is used, one with electron $\pTm > 23\,\GeV$ and muon $\pTm>8\,\GeV$ 
and one with muon $\pTm > 23\,\GeV$ and electron $\pTm > 13\,\GeV$, the object firing
the higher \pT~trigger leg needs to have a transverse momentum
of at least $24\,\GeV$ on top of the requirements already discussed. This avoids
events in the lower part of the trigger turn-on curve being selected.

In addition to the selection described so far,
 a topological selection is made on the $D_{\zeta}$ variable \cite{cdf-dzeta},
\begin{align}\label{eqn:mssm_em_dzeta}
D_{\zeta} = P_{\zeta} - 1.85 P_{\zeta}^{\text{vis}}, \notag \\
\text{where } P_{\zeta} = (\vec{p}_{\text{T},1}^{\text{  vis}} + \vec{p}_{\text{T},2}^{\text{  vis}} + E_{\text{T}}^{\text{miss}})\frac{\vec{\zeta}}{|\vec{\zeta}|}, \notag \\
\text{and } P_{\zeta}^{\text{vis}} = (\vec{p}_{\text{T},1}^{\text{  vis}}+\vec{p}_{\text{T},2}^{\text{  vis}})\frac{\vec{\zeta}}{|\vec{\zeta}|}.
\end{align}
This means $D_{\zeta}$ is defined as the projection of the transverse momenta of the visible tau decay products plus missing energy, \pT+\MET, onto 
the axis $\vec{\zeta}$, minus the projection of only the transverse momenta of the visible tau decay products onto this axis.
The axis $\vec{\zeta}$ is the axis that bisects
the directions $\vec{p}_{\text{T,1}}^{\text{  vis}}$ and $\vec{p}_{\text{T,2}}^{\text{  vis}}$
of the visible decay products in the transverse plane. This definition is illustrated in figure
\ref{fig:mssm_dzeta}a, with figure \ref{fig:mssm_dzeta}b showing the $D_{\zeta}$ distribution
for \emu events. The selection used, $D_{\zeta} > -20\,\GeV$, rejects $\ttbar$, \Wjets and di-boson
events. 
%The momentum of the neutrinos should not be in the opposite direction of the sum of the visible decay products
%as the neutrinos and visible tau decay products travel at small angles from the original tau.

\begin{figure}[h!]
\begin{center}
\subfloat[Reconstruction of $D_{\zeta}$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/PZeta.pdf}}
\subfloat[$D_{\zeta}$ distribution in \emu channel]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/pzeta_inclusive_em_2016.pdf}}
\end{center}
\caption[Reconstruction of the $D_{\zeta}$ variable and the $D_{\zeta}$ distribution
in the \emu channel.]{(a) Reconstruction of $D_{\zeta}$ \cite{cdf-dzeta} and (b) $D_{\zeta}$ distribution in the 
\emu channel \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_dzeta}
\end{figure}
~\clearpage
\subsection{Categorisation}
\label{sec:mssm_eventsel_categories}
As the analysis targets both the gluon fusion
and the b-associated production modes, 
the sensitivity to the signal can be increased by categorising
based on the number of b-tagged jets in the event.

\begin{figure}[h!]
\begin{center}
\subfloat[Number of jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_mt_2016_log.pdf}}
\subfloat[Number of b-tagged jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_mt_2016_log.pdf}}
\end{center}
\caption[Number of jets and number of b-tagged jets in the \mutau channel, 
with the signal overlaid.]{(a) Number of jets and (b) number of b-tagged jets in the \mutau channel. The gluon fusion signal (dashed
blue line) and b-associated signal (dashed purple line) are overlaid on the expected background distribution. The signals
are normalised to 100 times their \xsbr at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$
scenario. The signal-sensitive bins motivate the choice of categories.}
\label{fig:mssm_cats_mt}
\end{figure}
